Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2019-12-02 xrb/paper.tex
add convergence to the diffusion table

\usepackage{epsf,color,amsmath}

\usepackage{cancel}

@@

\begin{deluxetable}{rL}
	\tablecaption{\label{table:diffusion} Convergence of diffusion test problem.}
	\tablehead{\colhead{base resolution} & \colhead{L-inf error}}
	\startdata
\cutinhead{no refinement}
	32  & 5.995\times 10^{-3} \\
        64  & 1.477\times 10^{-3} \\
       128  & 3.664\times 10^{-4} \\
       256  & 9.139\times 10^{-5} \\
\cutinhead{one level of refinement}
        32  & 1.480\times 10^{-3} \\
        64  & 3.685\times 10^{-4} \\
       128  & 9.406\times 10^{-5} \\
       256  & 2.446\times 10^{-5} \\
	\enddata
	%
\end{deluxetable}

>>>>

\usepackage{epsf,color,amsmath}
\usepackage{multirow}
\usepackage{cancel}

@@

\begin{deluxetable}{rLc}
	\tablecaption{\label{table:diffusion} Convergence of diffusion test problem.}
	\tablehead{\colhead{base resolution} & \colhead{L-inf error} & \colhead{convergence rate\tablenotemark{a}}}
	\startdata
\cutinhead{no refinement}
	32  & 5.995\times 10^{-3} & \multirow{2}{*}{2.04} \\
        64  & 1.477\times 10^{-3} & \multirow{2}{*}{2.01} \\
       128  & 3.664\times 10^{-4} & \multirow{2}{*}{2.00} \\
       256  & 9.139\times 10^{-5} & \\
\cutinhead{one level of refinement}
        32  & 1.480\times 10^{-3} & \multirow{2}{*}{2.01} \\
        64  & 3.685\times 10^{-4} & \multirow{2}{*}{1.97} \\
       128  & 9.406\times 10^{-5} & \multirow{2}{*}{1.94} \\
       256  & 2.446\times 10^{-5} & \\
	\enddata
	%
\tablenotetext{a}{Convergence, $n$, is defined between 2 successive resolutions as $n = \log_2(e_{2h}/e_h)$,
 where $e_{2h}$ is the error for the coarser resolution run and $e_h$ is the error for the finer resolution run.}
\end{deluxetable}
